|

### 2020-07-06 paper.Rmd
re-working abstract

A different view on the curse of dimensionality emerges for dimension reduction and visualization methods. When working with low-dimensional linear projections from a high-dimensional parameter space, most projections will show approximately Gaussian distributions of the data, and observations start to pile near the center as dimensionality increases [@diaconis1984]. For high-dimension low-sample size data this results in "data piling", i.e. we can find directions along which all observations are in a single point [@10.2307/27639976,@10.1093/biomet/asp084]. These issues also persist with non-linear dimension reduction techniques. This is often referred to as the "crowding problem", which methods like t-Distributed Stochastic Neighbor Embedding (t-SNE) [@tsne] aim to alleviate.

>>>>

Paradoxically, the curse of dimensionality inverts for dimension reduction, and affects the resulting visualizations. For low-dimensional linear projections of a high-dimensional data, most projections will show approximately Gaussian distributions of the data, with observations concentrating in the center [@diaconis1984]. In projection pursuit, this motivated the development of indexes showing departure from normality. @10.2307/27639976,@10.1093/biomet/asp084 call this "data piling", and in extreme cases of high-dimension low-sample size data, all observations are in a single point. These issues also persist with non-linear dimension reduction techniques. This is often referred to as the "crowding problem", which methods like t-Distributed Stochastic Neighbor Embedding (t-SNE) [@tsne] aim to alleviate.
